%-------------------------
% Resume in Latex
% Author : Rodney Ndum
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Rodney Ndum} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:upon request}{upon request}
    $|$
    \faAt \hspace{.5pt} \href{mailto:rodney.ndum@pepperdine.edu}{rodney.ndum@pepperdine.edu}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/ndum}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/rndum}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://rodneyndum.com}{Research}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/@34.0415081,-118.7121709}{Malibu, California}
\end{center}


%----------- ACADEMIC EXPERIENCE -----------

\section{Academic Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Pepperdine University}{Malibu, California}
      {Assistant Professor in Finance}{Aug 2024 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Teach Financial Management.}
            \resumeItem{Teach Investments.}
        \resumeItemListEnd
  
    \resumeSubheading
      {Florida State University}{Tallahassee, Florida}
      {Instructor of Record}{Jan 2022 \textbf{--} May 2024}
        \resumeItemListStart
            \resumeItem{Taught Financial Modeling in Excel.}
            \resumeItem{Taught Corporate Finance.}
            \resumeItem{Teaching Assistant for Undergrad General Corporate Finance with 2000+ students annually.}
        \resumeItemListEnd
    
    \resumeSubheading
      {McKnight Brain Institute}{Gainesville, Florida}
      {Research Assistant}{Nov 2013 \textbf{--} Mar 2016}
        \resumeItemListStart
            \resumeItem{Built Machine Learning, Computer Vision applications for tracking rodent gait.}
            \resumeItem{Built hardware using FTIR technology to capture rodent gait.}
            \resumeItem{Presented research at largest neuroscience conference in world, SFN.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd


%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Florida State University
      }{Tallahassee, Florida}
      {Ph.D. in Business Administration: Finance;   \textbf{GPA: 3.93/4.00}}{Jul 2019 \textbf{--} May 2024}{}{}

    \resumeEducationHeading
      {Syracuse University
      }{Syracuse, New York}
      {Juris Doctorate;   \textbf{}}{Aug 2021 \textbf{--} May 2024}{}{}

    \resumeEducationHeading
      {University of Florida 
      }{Gainesville, Florida}
      {M.B.A. concentration in Strategy;   }{Aug 2015 \textbf{--} May 2017}
      {B.Sc. in Computer Science Engineering;   \textbf{(honors)}}{Jan 2012 \textbf{--} Dec 2014}
      

  \resumeSubHeadingListEnd

%----------- PUBLICATIONS -----------





%----------- Working Papers -----------

\section{Working Papers}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{The Effect of Local Stock Market Participation on Local Housing Prices}{ (with C. Dougal)} \\ \vspace{3pt}

        \textbf{The Consequences of Government Funding on Firms}{ } \\ \vspace{3pt}
        
        \textbf{Litigation Risk and Analyst Forecasts:}{ (with Y. Cheng)} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd


%----------- Research in Progress -----------

\section{Research in Progress}
\vspace{2pt}
\resumeSubHeadingListStart
  \small{\item{

      \textbf{Firm Geographic Distribution}{ (with C. Dougal)} \\ \vspace{3pt}

      \textbf{Dynamic Cross-sectional Asset Pricing}{ (with C. Goulding)} \\ \vspace{3pt}

      \textbf{The Broad Effects of Foreign Directed Investments}{ (with J. Dickinson and K. Wade )} \\ \vspace{3pt}

      \textbf{The Broad Effects of the Opioid Crisis}{ } \\ \vspace{3pt}
      
      \textbf{Sports Team Realignment and Corporate Affiliation}{ (with M. Buckwalter-Figueroa)} \\ \vspace{3pt}
      
      \textbf{Litigation Risk and SEO}{ (D. Autore) } \\ \vspace{3pt}
      
  }}
\resumeSubHeadingListEnd


%----------- Media Coverage -----------

\section{Media Coverage}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{FSU Office of Graduate Fellowships:}{ \emph{\href{https://ogfa.fsu.edu/graduate/rodney-ndum}{\color{blue}McKnight Fellowships induction}}} \\ \vspace{3pt}
        
        \textbf{Poets and Quants:}{ \emph{\href{https://poetsandquants.com/2016/05/04/meet-florida-warringtons-mba-class-2017/5/}{\color{blue}Spotlight: MBA Class of 2017}}} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd


%----------- Teaching  -----------

\section{Teaching}
\vspace{2pt}
\resumeSubHeadingListStart
  \small{\item{

      \textbf{Financial Modeling and Forecasting w/ Computers (Summer 2023)}{ Evaluation 4.86/5.0} \\ \vspace{3pt}
      
      \textbf{Financial Modeling and Forecasting w/ Computers (Summer 2022)}{ Evaluation 4.85/5.0} \\ \vspace{3pt}
      
      \textbf{Problems in Financial Management (Spring 2022)}{ Evaluation 3.76/5.0 \textbf{(1st and largest class - 64 students)}} \\ \vspace{3pt}
      
  }}
\resumeSubHeadingListEnd


%----------- RESEARCH PRESENTATIONS -----------

\section{Research Presentations}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {2021}{}
      {}{}
        \resumeItemListStart
            \resumeItem{\textbf{Florida State University} 2nd Year Paper}
        \resumeItemListEnd
    
    
  \resumeSubHeadingListEnd



%----------- ACADEMIC SERVICE  -----------

\section{Academic Service}
\vspace{2pt}
\resumeSubHeadingListStart
  \small{\item{
      
      \textbf{Vice President: FEDSA}{ The PhD Project, 2022 } \\ \vspace{3pt}
      
      \textbf{Research and Media Facilitator}{ The PhD Project, 2021} \\ \vspace{3pt}
      
  }}
\resumeSubHeadingListEnd


%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{McKnight Fellowship:}{ 2022 Graduate Student Fellow} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- INDUSTRY EXPERIENCE -----------

\section{Industry Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

  \resumeSubheading
  {The Jacobsen}{Austin, Texas}
  {Commodities Research Analyst }{ 2018 \textbf{--} 2019}
    \resumeItemListStart
        \resumeItem{Automated data sourcing saving approximately 20 weekly man hours and improving data accuracy.}
        \resumeItem{Supported building of weekly marketing report sold to hedge funds.}
        \resumeItem{Created futures price forecasts for Soybean complex.}
    \resumeItemListEnd
  
    \resumeSubheading
      {Meta Platforms, Inc (Facebook)}{Austin, Texas}
      {Project Manager IV }{ 2017 \textbf{--} 2018}
        \resumeItemListStart
            \resumeItem{Supported 2 billion Facebook and 800 million Instagram users.}
            \resumeItem{Worked with engineering to create Machine Learning training sets.}
            \resumeItem{Queried Big Data systems with Python and SQL to generate insights.}
        \resumeItemListEnd

    
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Aegus Analytics} $|$ \emph{\href{https://github.com/orgs/Aegus-Analytics}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Provides unified source for publicly available data.}
            \resumeItem{Cleans data for easy joins with common academic data sources.}
            \resumeItem{Provides data query features to sample data before use.}
            \resumeItem{Provides data visualization and automated alerts and reporting to track trends.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Academia Python Library} $|$ \emph{\href{https://github.com/rndum/aegus-academia}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Library which modularizes commonly used academic classification such as Fama French industry.}
            \resumeItem{Promotes reproducibility and reduces human error by providing standardized pre-coded classifications.}
          \resumeItemListEnd
    
      
    \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ Python, STATA, SQL, LATEX, VBA, Google Script, DBT, Tableau} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Git, Arduino, Cloud Computing, VM, VSCode, Apache Spark, Apache Superset, Apache Druid} \\ \vspace{3pt}

        \textbf{Platforms:}{ WRDS, Data.Gov, BEA, Zillow, FEC, NETS, HMDA} \\ \vspace{3pt}
        
        \textbf{Languages:}{ English (Native), Spanish (Elementary)}
        
    }}
  \resumeSubHeadingListEnd



%----------- REFERENCES -----------

\section{References}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Dr. Casey Dougal: Associate Professor}{ Department of Finance, Florida State University, Phone: 850-644-2038, Email: cdougal@business.fsu.edu} \\ \vspace{3pt}

        \textbf{Dr. Yingmei Cheng: Professor}{ Department of Finance, Florida State University, Phone: 850-645-7869, Email:  ycheng@business.fsu.edu} \\ \vspace{3pt}

        \textbf{Dr. William Christiansen: Truist Associate Professor}{ Department of Finance, Florida State University, Phone: 850-644-8202, Email:   wchristiansen@business.fsu.edu} \\ \vspace{3pt}

    }}
  \resumeSubHeadingListEnd


\end{document}
